\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Mention simulated censorship in abstract.

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. We conducted a series of 
experiments to improve the Tor launcher configuration interface, which configures network components
that circumvent censorship. A 16-participant experiment and interview
identifies common user struggles while circumventing censorship.
We use as feedback to redesign the configuration interface.
We test the impact of our
changes on 124 participants to find that our changes results in a significant reduction 
in the spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

>>>>

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool.
We conducted a series of
experiments to evaluate and improve the configuration interface of Tor Browser,
placing users in a simulated censorship environment and measuring their ability to circumvent it.
A 16-participant experiment and interview
identifies common user struggles while circumventing censorship.
We use as feedback to redesign the configuration interface.
We test the impact of our
changes on 124 participants to find that our changes results in a significant reduction 
in the spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}
